\documentclass[]{article}
\usepackage[]{comment}
\usepackage[]{color}
\usepackage[]{enumitem}
\usepackage[colorlinks=true]{hyperref}
\usepackage[]{graphicx}
\usepackage[]{fancyhdr}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{fixltx2e}
\usepackage{mathtools} 
\usepackage{amsmath}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lhead{} %header
\chead{}
\rhead{}
\lfoot{This document was written using \LaTeX} %footer
\cfoot{}
\rfoot{\thepage}
\fancypagestyle{mystyle}
{\fancyhf{}
\renewcommand{\headrulewidth}{1pt}
\fancyhead[l]{}
\fancyhead[c]{}
\fancyhead[r]{}
\fancyfoot[l]{This document was written using \LaTeX}
\fancyfoot[c]{}
\fancyfoot[r]{\thepage}}
\renewcommand{\footrulewidth}{1pt}
\title{Sridhar Vempati}
\author{sridharvempati@cuk.ac.in | vempatisridharbzy@gmail.com}
% Page starts here-------------------------------------------------------------------------------
\begin{document}
    \begin{center}
        \Huge \textbf{Sridhar Vempati}\\
	   \large AIR 2007 EC GATE'22 \(|\) 3\textsuperscript{rd} year ECE Student \\
        %\large sridharvempati@cuk.ac.in | vempatisridharbzy@gmail.com\\ 
	   \large Looking for internships in the field of VLSI Design, Embedded Systems, DSP, IoT, 3D Printing, PCB Designing, CAD \& Internet of Things.
    \end{center}

    \begin{multicols}{2}[]
      \begin{flushleft}
	 sridharvempati@cuk.ac.in \\ vempatisridharbzy@gmail.com
      \end{flushleft}
      \begin{flushright}
	Contact No.: +91 9440240316\\
	+91 7624922503
        \end{flushright}
    \end{multicols}  
    
    \begin{spacing}{0.05} %double line
    \noindent
    \rule{\linewidth}{2pt}
    \rule{\linewidth}{1pt}  
    \end{spacing}

\section*{\color{blue}{Summary}}%Summary
I am Sridhar Vempati and I am currently pursuing B.Tech 3\textsuperscript{rd} year in Electronics \& Communication Engineering from \textbf{Central University of Karnataka}. I have an overall percentage of \textbf{89.2\%} in Engineering(upto 4\textsuperscript{th} semester). I secured \textbf{AIR 2007 in the GATE 2022 EC with a score of 508 and 37.67 marks}. I was awarded the \textbf{NPTEL Enthusiast} Certificate for having completed 8 NPTEL courses. My interests lie in VLSI Design, Embedded Systems, SoC Design, IoT, CAD, DSP.\\Previously, I worked as Real Time Embedded Systems and Mechatronics Intern at Robocoupler Pvt. Ltd., Internet of Things Intern at Verzeo Pvt. Ltd. and Python Project Development Intern in Codespeedy Technology.\\\\
	\textbf {Find my GATE Scorecard \href{https://drive.google.com/drive/folders/11RDjP2MJ5MHqZlXpzrzX8gFm-TfcGO2r?usp=sharing}{\em here}}\\
     \textbf{LinkedIn Profile: }{\em \url{https://www.linkedin.com/in/sridhar-vempati/}}\\
     \textbf{GitHub Profile: }{\em \url{https://github.com/Sridhar1502}}\\
	\textbf{Coderspeedy Profile: }{\em \url{https://coderspacket.com/contributor/vempatisridharbzy}}
\section*{\color{blue}{Education}}%Education
    \begin{itemize}
        \item \textbf{Bachelor of Technology (B.Tech), Electronics and Communication} \\Central university of Karnataka \\2019 - 2023 \\Percentage: 89.2\% (upto 4\textsuperscript{th} semester)
	   \item \textbf{Senior Secondary (XII), Science} \\Tirumala Jr. College\\BOARD OF INTERMEDIATE EDUCATION , ANDHRA PRADESH (BIEAP)\\Year of completion: 2019\\CGPA: 9.73
	  \item \textbf{Secondary (X)} \\Bhashyam E.M School\\BOARD OF SECONDARY SCHOOL EDUCATION, ANDHRA PRADESH (BSEAP)\\Year of completion: 2017\\ CGPA: 10.00
    \end{itemize} 
\section*{\color{blue}{Internships}}%Experience
    \begin{itemize}
    \item \textbf{Realtime Embedded Systems and Mechatronics Intern}\\Robocoupler Pvt. Ltd., Virtual (May 2021 - Sep 2021)\\During this Internship, my team and I developed Map making technology for Automatic Docking System of the Cleaning Robots using different approaches such as Machine learning Approach,  Algorithmic Approach, Sensors and Bluetooth Approach and using RFID Technology. Find this project report \href{https://docs.google.com/document/d/1VjMvaT-iSSNu5BvjKKVbp-ZArXbTHrDEdOdBbaB3qdw/edit?usp=sharing}{\em here}.
	\item \textbf{Internet of Things Intern}\\Verzeo Pvt. Ltd., Virtual (Aug 2020 - Sep 2020)\\During this internship, I learnt about different development boards viz Arduino Uno, ESP-32, Zigbee and GSM. I built an Voice Controlled Home Automation System using these development boards where we can control home electronic appliances such as lights and fans using Google Assistant and IFTTT Web Application.
    	\item \textbf{Python Project Development Intern}\\Codespeedy Technology, Virtual (Jul 2020 - Aug 2020)\\During this Internship, I developed and published python projects viz. Vocabulary Quiz using Python Data Structures, Word Cloud Using Python. You can find my Codespeedy dashboard \href{https://coderspacket.com/contributor/vempatisridharbzy}{\em here}.\\ \\
\textbf{All the Internship Certificates are available }\href{https://drive.google.com/drive/u/0/folders/1X2hJOIpAaPBdThqYgYWMJrkt0Hddwq_q}{\em here}
    \end{itemize}
    %\newpage
\section*{\color{blue}{NPTEL Certifications}}
    \begin{itemize}
    \begin{multicols}{2}
      \item System Design Through VERILOG (85\%)
	 \item Embedded System Design with ARM (83\%)
	 \item Control Systems (74\%)
	 \item Digital Circuits (72\%)
	 \item Hardware modelling Using Verilog (68\%)
	 \item Computer Architecture (63\%)
      \item Switching Circuits and Logic Design (58\%)
      \item Introduction to Embedded System Design (51\%)
    \end{multicols}
    \end{itemize}
  \subsection*{Ongoing NPTEL Certification courses}
    \begin{itemize}
    \begin{multicols}{2}
      \item VLSI Physical Design
	 \item Network Analysis
	 \item Microprocessors and Microcontrollers
	 \item Effective Writing
    \end{multicols}
    \end{itemize}
%Skills
\section*{\color{blue}{Skills}}
    \begin{itemize}
    \begin{multicols}{3} 
        \item Arduino programming
	   \item Internet of Things
	   \item Python 
	   \item VERILOG
        \item C Programming
	   \item CAD
	   \item Embedded C
	   \item MATLAB
	   \item LaTeX
    \end{multicols}
    \end{itemize}
%Courses
    \section*{\color{blue}{Additional Courses}}
    \subsection*{MATLAB Courses}
    \begin{itemize}
    \begin{multicols}{2}
        \item MATLAB Onramp
        \item Machine Learning Onramp
        \item Introduction to Linear Algebra with MATLAB
    \end{multicols}
    \end{itemize}
    \subsection*{Coursera}
    \begin{itemize}
    \begin{multicols}{2}
        \item Crash Course on Python
        \item Python Data Structures
        \item Introduction to HTML5
        \item Logistic Regression with NumPy and Python
    \end{multicols}
    \end{itemize}
%\subsection*{Coursera Projects}
 %\begin{itemize}
 %   \begin{multicols}{2}
   	%\item{Python Data Structures}
    	%\item{Logistic Regression with NumPy and Python}
%	\item{Build Your Portfolio Website with HTML and CSS}
 	%\item{Machine Learning: Predict Numbers from Handwritten Digits using a Neural Network, Keras and R}
 	%\item{Image Classification with CNNs using Keras}
 	%\item{Google Ads for Beginners}
 	%\item{Computer Vision - Object Tracking with OpenCV and Python}
 %\end{multicols}
 %\end{itemize}
\begin{comment}

\section*{\color{blue}{Workshops/Seminars/Webinars Attended}}
\begin{itemize}
  \item Webinar on \textbf{Benefits of IEEE Membership} held by IEEE Student branch Central University of Karnataka on 21st August 2020.
      \item Webinar on\textbf{ Deep Learning Based Video Analytics For Surveilnace IOT Applications} held by IEEE Computer Society CHAPTER -HYDERABAD Section on 6th August 2020
      \item Webinar on \textbf{Art of Success for Civil Services} organised by Department of Electronics and Communication Engineering, Hirasugar Institute of Technology, Nidasoshi in association with ALS Satellite Education, Delhi on 11th July 2020.
      \item One day Workshop on \textbf{LaTeX} at University of Hyderabad held on 29th Feb 2020 conducted by IEEE Hyderabad Section.
     \item Expert Lecture Series on \textbf{Machine Learning, Internet of Things, Artificial Intelligence, Cloud \& Data Analytics}
      held on 9th August 2019 by IEEE Computer Society, Central University of Karnataka
  \end{itemize}
\end{comment}
   % \newpage
   % \section*{Memberships}
   % \begin{itemize}
   %     \item \textbf{Institute of Electrical and Electronics Engineering (IEEE)}\hspace{2.95cm}2019-present\\ IEEE Membership No. - 96100611\\ Student Branch Central University of Karnataka
   %     \item \textbf{International Association of Engineers (IAENG)}\hspace{4.66cm}2020-present\\ Membership No. - 254271
   %     \item \textbf{National Society of Professional Engineers (NSPE)}\hspace{4.186cm}2020-present\\ Membership No. - 300752046
   % \end{itemize}
\section*{\color{blue}{Awards/Participations/Selections}}
   \begin{itemize}
   \item \textbf{Got selected in First Round of National Engineering Olympiad 3.0} held from 24th April 2020 to 28th April 2020. Selected to Second Round. Find the Certificate \href{https://drive.google.com/drive/u/0/folders/1afmjGeQ6c10q58FP6xpgcYjkM3Um7R69}{\em here}
     \item \textbf{Got 2nd Prize for Home Automation using Voice Control by Arduino Uno} Project in Techno-Nirman 2019 conducted by School of Engineering, Central University of Karnataka on 15th August 2019. Find the certificate \href{https://drive.google.com/file/d/1gPYqmU3ETYQdZBCdEvzVyUp55GT4LPBs/view?usp=sharing}{\em here}
   \end{itemize}
\section*{\color{blue}{Other Links}}
    \begin{itemize}
	\item Find my GATE Scorecard \href{https://drive.google.com/drive/folders/11RDjP2MJ5MHqZlXpzrzX8gFm-TfcGO2r?usp=sharing}{\em here}
    \item You can find all my Internship certificates, NPTEL Certificates and Additional Courses Certificates \href{https://drive.google.com/drive/folders/1afmjGeQ6c10q58FP6xpgcYjkM3Um7R69?usp=sharing}{\em here}
    \item I have done some Coursera Projects in Coursera project Network. Find the certificates \href{https://drive.google.com/drive/u/0/folders/187CiSJKh_43Vlr-XUnmirNDy3oFicABx}{\em here}.
    \end{itemize}

\end{document}